Risk Perceptions for Wearable Devices

### 2015-03-05 tex-inputs/results-regression.tex
Fix multiply defined labels

We created several models using two independent variables as predictors: data recipient and data type. Because the device type independent variable (i.e., whether they were using the Cubetastic3000 or a smartphone) was only varied for the 5 smartphone misbehaviors listed in Section \ref{sec:smartphones}, we removed these 5 data types from our models, which resulted in a total of 72 data types shared between 4 possible recipients. We also used our collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score. For each model, we performed Wald's test to examine the model effects attributable to each of these parameters and observed that the only covariates that had an observable effect on our models were gender and participants' IUIPC scores, which also exhibited an interaction effect with each other. Thus, we opted to remove the other covariates from our analysis. Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit). As can be seen, the data type was the strongest predictor of VUR. The coefficients for the model with the best fit can be seen in Appendix \ref{sec:regression}.

@@

Using these two new variables as additional independent variables (and removing the previous data type variable), we created a second set of models. Because these risk categories and mediums are less likely to change over time, models that take these into account are likely to be more useful and less likely to be overfit. What these models show us is that both risk and medium are relatively strong predictors by themselves, and have an even stronger interaction effect. When the data recipient and covariates are added to the model, the resulting goodness-of-fit is not much worse than that of the model using the actual data type. The full model can be found in Appendix \ref{sec:regression2}.

>>>>

We created several models using two independent variables as predictors: data recipient and data type. Because the device type independent variable (i.e., whether they were using the Cubetastic3000 or a smartphone) was only varied for the 5 smartphone misbehaviors listed in Section \ref{sec:smartphones}, we removed these 5 data types from our models, which resulted in a total of 72 data types shared between 4 possible recipients. We also used our collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score. For each model, we performed Wald's test to examine the model effects attributable to each of these parameters and observed that the only covariates that had an observable effect on our models were gender and participants' IUIPC scores, which also exhibited an interaction effect with each other. Thus, we opted to remove the other covariates from our analysis. Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit). As can be seen, the data type was the strongest predictor of VUR. The coefficients for the model with the best fit can be seen in Appendix \ref{sec:regression-apx}.

@@

Using these two new variables as additional independent variables (and removing the previous data type variable), we created a second set of models. Because these risk categories and mediums are less likely to change over time, models that take these into account are likely to be more useful and less likely to be overfit. What these models show us is that both risk and medium are relatively strong predictors by themselves, and have an even stronger interaction effect. When the data recipient and covariates are added to the model, the resulting goodness-of-fit is not much worse than that of the model using the actual data type. The full model can be found in Appendix \ref{sec:regression-apx2}.
